What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-29 android-stacks.tex
changes along the paper

%Among the issues defined on issue trackers, we can find issues reporting bugs, and system crashes 
%found as a result of application executions. Such issues usually contain exception stack traces [ref][ref].

<SUCH ISSUES INCLUDE STACK TRACES. WHAT IS THE RELATION BETWEEN STACK TRACE AND CRASH>
<stack traces are part of good issues....>

@@

When available, exception stack traces provides a useful source of information about system crashes and 
 can enable different kinds of post-mortem analysis, such as:   debugging~\cite{schroter2010stack}, 
 bug classification and clustering ~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},  
automated bug fixing ~\cite{sinha2009fault} and fault-proneness prediction models analysis ~\cite{kim2013predicting}.

Most of such studies, however, focused the analysis on one or two system at a time. None 
of them targeted a family of applications (sharing a common framework) aiming at extracting 
the common characteristics of crash information and checking whether they could provide
insights on  similar vulnerabilities on the applications and underlaying framework.

In this work, we perform the first post mortem analysis of the exception stack traces embedded on all issues
created on Android projects available in GitHub and Googlecode. Using a custom tool called ExceptionMiner,
 which we develop specifically for this study, we mine stack traces from issues across all Android projects on
GitHub and Googlecode. Overall, we analyzed the XXXX issues extracted from on XXX Android projects defined in
GitHub and XXX projects defined in Googlecode. From these issues,  XXX stack traces were extracted and used as
 a source of information for our analysis. The stack trace analysis was augmented by additional information
extracted from JDK, Android SO and Android SDK and the applications using byte code and source code analysis.
 Manual inspection was used to leverage the understanding of exception stack traces and support further discussions and insights.

@@

   \item  A multitude of programming mistakes were reported as the main causes of stack traces:
  41,1\%  (12,625)  of reported stack traces were caused by programming mistakes; and 26,31\% of analyzed stack traces reported a java.lang.NullPointerException as root cause;

   \item 1,671 projects (44,47\%) contained at least one issue reporting a java.lang.NullPointerException as the root cause of a stack trace.

@@

   \item  The development model of Android platform (strongly based on system call-backs) encouraged 
     the use of general RuntimeExceptions.

  %\item  Issues reporting uncaught checked exceptions.

@@

Although the study focused on Android opensource applications, some of the results are not restricted to this context, 
for instance: some of the unexpected wrappings were performed by Java libraries and elements (e.g. reflection library and 
the static blocks); and the undocumented runtime exceptions were also found in Java libraries beyonds the Android plaftorm.
The study results are relevant to: (i) Android and Java developers to familiarize with the most common reported exceptions 
mis-uses which is the first step to help developers to avoid making them; (ii) designers of languages to consider ways of reducing the abundance of NullPointerExceptions; and (iii) tool designers to consider developing tools that enable a cross-project defect analysis.

@@

  \item  It presents the the exploratory study methodology to ..... (complete - view the reviewer comment)

>>>>

%Among the issues defined on issue trackers, we can find issues reporting bugs, and system crashes 
%found as a result of application executions. Such issues usually contain exception stack traces [ref][ref]. 
%<SUCH ISSUES INCLUDE STACK TRACES. WHAT IS THE RELATION BETWEEN STACK TRACE AND CRASH>
%<stack traces are part of good issues....>

@@

When available, exception stack traces provides a useful source of information about system crashes ~\cite{bettenburg2008makes} which 
 can enable different kinds of post-mortem analysis to support:  debugging~\cite{schroter2010stack}, 
 bug classification and clustering ~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},  
automated bug fixing ~\cite{sinha2009fault} and fault-proneness prediction models ~\cite{kim2013predicting}.

Most of such studies, however, focused the analysis on one or two system at a time.
This paper reports an exploratory study which targets a family of applications 
(sharing the common Android framework) aiming at extracting 
the common characteristics of exception stack traces reported to such systems to provide
insights on similar fragilities on the exception related code of the applications and underlaying framework.

To do so we perform a post mortem analysis of the exception stack traces embedded on all issues
created on Android projects available in GitHub and Googlecode. Using a custom tool called ExceptionMiner,
 which we develop specifically for this study, we mine stack traces from issues across all Android projects on
GitHub and Googlecode. Overall, we analyzed the XXXX issues extracted from on XXX Android projects defined in
GitHub and XXX projects defined in Googlecode. From these issues,  XXX stack traces were extracted and used as
 a source of information for our analysis. The stack trace analysis was augmented by additional information
extracted from JDK, Android SO and Android SDK and the applications using byte code and source code analysis.
 Manual inspection was used to leverage the understanding of exception stack traces and support further discussions and insights.

%projects: 788	 - projects with issues - 724 - 
%projects with issues (with exceptions): 243 
%projects with stacks: 158  -  stacks: 3559 (defect)
%Github: issues: 50342 - stacks: 3865 - projects: 2542 - projects with stacks: 293

@@

@@

   \item Undocumented checked exception signaled by native Android library. This finding points to a fragility 
on the way exceptions on JNI interface funcions, which can lead to uncaught exceptions that are difficult do 
debug.

  \item  A multitude of programming mistakes were reported as the main causes of stack traces:
 XXX  of reported stack traces were caused by programming mistakes; and XXX of analyzed stack traces reported a java.lang.NullPointerException as root cause;

@@

Such fragilities represent obstacles to the development of dependable mobile apps as well as other Java-based systems
as they share the same exception model. Although the study focused on Android opensource applications, some of the results are not restricted to this context, 
for instance: some of the unexpected wrappings were performed by Java libraries and elements (e.g. reflection library and 
the static blocks); and the undocumented runtime exceptions were also found in Java libraries besides the Android plaftorm.
The study results are relevant to: (i) Android and Java developers to familiarize common characteristics and fragilities of exception-related code 
which is the first step to help developers preventing and dealing with them; (ii) designers of languages and tools to consider ways of reducing 
such fragilities in Android and Java environments.

@@
